Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-03-01 paper-webserver.tex
ADD: touching on patric

\mwcomment{I would suggest we avoid the comparison to sequence databases or genome sequence platforms (e.g. assembly, gene annotation etc). We really don't have the capacity to replace EnteroBase, Genbank, IRIDA, etc. I see Spfy as a repository of E.coli phenotypes important for public health. It allows users to rapidly predict phenotypes and retrieve the phenotypes of historical strains to: track trends, observe context amoung evolutionary related strains, identify biomarkers, etc. In other words, Spfy provides WGS-based phenotypes + big picture comparative genomics. The big picture is only possible by 1. recomputing everything everytime, or 2. storing the results as genomes are analysed. With size of WGS data, option 2 is only viable option}
\mwcomment{Title may need work. Should it mention comparative genomics? Can't be too long thou}
\title{Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative genomics}

@@

Comprehensive platforms that combine individual programs into a cohesive whole also exist. These include free platforms such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial}, and the Pathosystems Resource Integration Center (PATRIC) \cite{wattam2013patric}. Commercial applications, such as Bionumerics, which is used by PulseNet International for the analyses of WGS data in outbreak situations also exist, and offer support as well as accredited, standardized tests \cite{swaminathan2001pulsenet}. These platforms are designed to be applied to individual projects \cite{}.

@@

>>>>

\mwcomment{I would suggest we avoid the comparison to sequence databases or genome sequence platforms (e.g. assembly, gene annotation etc). We really don't have the capacity to replace EnteroBase, Genbank, IRIDA, etc. I see Spfy as a repository of E.coli phenotypes important for public health. It allows users to rapidly predict phenotypes and retrieve the phenotypes of historical strains to: track trends, observe context amoung evolutionary related strains, identify biomarkers, etc. In other words, Spfy provides WGS-based phenotypes + big picture comparative genomics. The big picture is only possible by 1. recomputing everything everytime, or 2. storing the results as genomes are analysed. With size of WGS data, option 2 is only viable option}
\mwcomment{Title may need work. Should it mention comparative genomics? Can't be too long thou}
\title{Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses}

@@

Comprehensive platforms that combine individual programs into a cohesive whole also exist. These include free platforms such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial}, and the Pathosystems Resource Integration Center (PATRIC) \cite{wattam2016improvements}. Commercial applications, such as Bionumerics, which is used by PulseNet International for the analyses of WGS data in outbreak situations also exist, and offer support as well as accredited, standardized tests \cite{swaminathan2001pulsenet}. These platforms are designed to be applied to individual projects \cite{}.

@@

PATRIC \cite{wattam2016improvements} adds support for comparing user-submitted genomes and pre-analyzed public data, enabling comparisons of gene annotations for user-submitted genomes against reference genomes. PATRIC indexes a NoSQL document store to comparison similar document types. Unlike PATRIC which is targeted towards comparative genomics, Spfy's graph database enables broader generic comparisons against any population groupings. For example, Spfy can compare all genomes with a particular subtype for gene annotations, source metadata for gene annotations, or any two (or more) node or attribute data.

\small \input{tables/comparison}
